The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-15 paper/discussion.tex
add bibtex citations; update model #4 figure

\paragraph{How has binarity been considered in occurrence rate measurements?}
Binarity introduces systematic uncertainty to star and planet counts, and also 
to estimates of pipeline completeness.
In spite of this fact, stellar multiplicity has mostly been ignored in 
calculations of planet occurrence rates using transit survey data\footnote{
    An online list of occurrence rate papers is maintained at 
    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
}~({\it 
e.g.}, Howard et al. 2012, Fressin et al., 2013, Foreman-Mackey et 
al., 2014, Dressing \& Charbonneau 2015, and Burke et al. 2015).
For {\it Kepler} occurrence rates specifically, it seems that no one has yet 
carefully assessed the magnitude of the issue.
While we do not resolve the problem, we do suggest
the approximate scale of the necessary corrections in a survey-independent 
manner.

Of course, on a system-by-system level stellar multiplicity affects the 
interpretation of planet candidates. High resolution imaging 
campaigns have measured the multiplicity of almost all {\it Kepler}\ Objects 
of Interest 
(Howell et al. 2011; Adams et al. 2012, 2013; Horch et al. 2012, 2014; 
Lillo-Box et al. 2012, 2014; Dressing et al. 2014; Law et al. 2014; Cartier et 
al. 2015; Everett et al. 2015; Gilliland et al. 2015; Wang et al. 2015a, 
2015b; Baranec et al. 2016).
The results of these programs have been collected by Furlan et al. 
(2017), and they represent an important advance in understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's effects 
on the mass-radius diagram (Furlan \& Howell 2017).

The high resolution imaging campaign is also beginning to connect with
occurrence rate calculations.
The most recent rate studies have used Furlan et al. (2017)'s 
catalog to test the effects of removing KOI hosts with known companions, which 
helps reduce contamination in the ``numerator'' of 
the occurrence rate (Fulton et al. 2017, Petigura et al., in prep).
However, without an understanding of the multiplicity statistics of the 
non-KOI stars, the true completeness, and thus the true 
occurrence rates, will remain biased.
The first-order correction that we suggest, given the impracticality of 
performing high-resolution imaging of every selected star in a transit survey,
is to model the detection pipeline's efficiency while accounting for 
binarity.
%Simply put~--~do not assume binarity can be ignored, and take the relevant 
%systematic uncertainties about the selected stars into account.
For {\it Kepler}, this would require high resolution imaging of a
comparison sample of non-KOI host stars. If the associated multiplicity 
statistics are then included in a model of the pipeline's detection 
efficiency, and the number of selected stars is appropriately counted, it 
would correct most of binarity's biases.

\paragraph{The hot Jupiter rate discrepancy}
There is at least one context in which ignoring binarity may already be 
leading to discrepant measurements.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
The discrepancy has weak statistical significance ($<3\sigma$).
One reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by Gould et al. (2006), the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant planets (Santos et al 2004, Fischer and Valenti 2005).
The {\it Kepler}\ sample specifically has been measured to be more metal poor 
than the local neighborhood, with a mean metallicity of $[{\rm M/H}]_{\rm 
    mean}\approx -0.05$ (Dong et al., 2014; Guo et al., 2017).
Studying the problem in detail, Guo et al. recently argued that the 
metallicity difference could account for a $\approx 0.1\%$ difference in the 
measured rates between the CKS and {\it Kepler}\ samples~--~not a $\approx 
0.5\%$ difference.
Guo et al. concluded that ``other factors, such as binary contamination and 
imperfect stellar properties'' must also be at play.

Aside from surveying stars of varying metallicities, radial velocity and 
transit surveys differ in how they treat binarity.
Radial velocity surveys typically reject both visual and spectroscopic binaries
({\it e.g.}, Wright et al. 2012).
Transit surveys typically observe binaries, but the question of whether they 
were searchable to begin with is left for later interpretation.
In spectroscopic follow-up of candidate transiting planets, the prevalence of 
astrophysical false-positives may also lead to a bias against confirmation of 
transiting planets in binary systems.

@@

To assess the effect this might have towards resolving the hot Jupiter rate 
discrepancy we ask:
what is the probability of Wright et al. (2012)'s result, given a rate drawn 
from the stated bounds of Petigura et al. (in prep)? (See 
Table~\ref{tab:hj_rates}).
In other words, we first take the true HJ rate per thousand stars as 
$\Lambda_{\rm HJ} = 5.7 \pm 1.3$, with Gaussian uncertainties. 
We then draw from a Poisson distribution and compute the probability of 
detecting at least 10 hot Jupiters in a sample of 836 stars.
Without accounting for binarity or metallicity, only 4\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account for Guo et al. 
(2017)'s measured metallicity difference between the {\it Kepler}\ field and 
the local solar neighborhood, 9\% of RV surveys would detect at least 10 hot 
Jupiters.
If we multiply once more by $1.3$ to account for binarity's bias, we find that
23\% of RV surveys would detect at least 10 hot Jupiters, and any discrepancy 
would be rather tenuous.
We emphasize that this result is only suggestive~--~a true resolution of the 
rate discrepancy would likely require a detailed understanding of the {\it 
Kepler}\ field's multiplicity statistics.

\paragraph{The rate of Earth analogs}
Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
orbiting Sun-like stars has been independently measured by Youdin, Petigura, 
Dong \& Zhu, Foreman-Mackey et al., and Burke et al. (2011, 2013, 2013, 2014, 
and 2015 respectively).
These efforts have found that the one-year terrestrial planet occurrence rate 
varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
assumptions that are made when retrieving the rate (Burke et al. 2015's 
Fig.~17).
In our Model \#3, the inferred rate is $\approx 0.84\times$ the true rate 
around single stars.
This bias is quite small compared to the other systematic factors that 
currently dominate the dispersion in $\eta_\oplus$ measurements.
If a future transit survey measures an absolute value of $\eta_\oplus$ to 
better than a factor of two, binarity might merit closer attention.

\paragraph{The CKS radius gap}
By improving the stellar radii... {\bf TODO}
%TODO DO THESE CALCULATIONS

\paragraph{Does a detected planet orbit the primary or secondary?}
Ciardi et al. (2015) studied the effects of stellar multiplicity on the 
planet radii derived from transit surveys.
They modeled the problem for {\it Kepler}\ objects of interest by matching a 
population of binary and tertiary companions to KOI stars, 
under the assumption that the KIC-listed stars were the primaries.
They then computed planet radius correction factors assuming that {\it 
Kepler}-detected planets orbited the primary or companion stars
with equal probability (their Sec. 5).
Under these assumptions, they found that any given planet's radius is on 
average underestimated by a multiplicative factor of 1.5.

Our models show that assuming a detected planet has equal probability of 
orbiting the primary or secondary leads to an overstatement of
binarity's population-level effects.
A planet orbiting the secondary does lead to extreme corrections, but these 
cases are rare outliers, because the searchable volume for secondaries is so 
much smaller than that for primaries.
Phrased in terms of the completeness, in our Model \#3 only $\sim 6\%$ of 
selected secondaries are searchable, compared to $\sim 60\%$ of selected 
primaries.
This means that when high-resolution imaging discovers a binary companion in 
a system that hosts a detected transiting planet, the planet is much
more likely to orbit the primary.
This statement is independent of the fact that planets are often confirmed to 
orbit the primary by inferring the stellar density from the transit duration.

\paragraph{On the utility for future occurrence rate measurements}
{\it TESS}\ is expected to discover over $10^4$ giant planets (Sullivan 
et al. 2015).
Though they will be difficult to distinguish from false positives, one 
possible use of this overwhelmingly large sample will to measure an
occurrence rate of short-period giant planets.
Our work indicates that if this measurement is to be more accurate than $\sim 
30\%$, binarity cannot be neglected.

\paragraph{Independent approaches for estimating binarity's effects}
T. Barclay et al. (in prep) have performed the exercise of taking stars 
selected by the {\it Kepler}\ team, pairing them with a population of 
secondaries, injecting a realistic distribution of planet radii, 
and then comparing the inferred occurrence rates with the true ones.
In their model, they find that binarity leads to an inferred rate of 
Earth-sized planets $\approx 10\%$ less than the true rate.
In our Model \#3, if all $Z_i$'s are equal (a plausible assumption in 
the lack of evidence to the contrary), the underestimate is by a comparable 
16\%.

>>>>

\paragraph{How has binarity been considered in occurrence rate measurements?}
Binarity introduces systematic uncertainty to star and planet counts, and also 
to estimates of pipeline completeness.
In spite of this fact, stellar multiplicity has mostly been ignored in 
calculations of planet occurrence rates using transit survey data\footnote{
    A list of occurrence rate papers is maintained at 
    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
}~
\citep[\textit{e.g.},][]{howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,dressing_occurrence_2015,burke_terrestrial_2015}.
For {\it Kepler} occurrence rates specifically, it seems that no one has yet 
carefully assessed binarity's importance, or lack thereof.
While we do not resolve the problem, we do suggest
the approximate scale of the necessary corrections in a survey-independent 
manner.

Of course, on a system-by-system level stellar multiplicity affects the 
interpretation of planet candidates. High resolution imaging 
campaigns have measured the multiplicity of almost all {\it Kepler}\ Objects 
of Interest 
\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016}.
The results of these programs have been collected 
by~\citet{furlan_kepler_2017}, and they represent an important advance in 
understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's effects 
on the mass-radius diagram~\citep{furlan_densities_2017}.

The high resolution imaging campaign is also beginning to connect with
occurrence rate calculations.
The most recent rate studies have used~\citet{furlan_kepler_2017}'s 
catalog to test the effects of removing KOI hosts with known companions, which 
helps reduce contamination in the ``numerator'' of 
the occurrence rate (\citealt{fulton_california-_2017}; Petigura et al.\! 2018,
in preparation).
However, without an understanding of the multiplicity statistics of the 
non-KOI stars, the true completeness, and thus the true 
occurrence rates, will remain biased.
The first-order correction that we suggest, given the impracticality of 
performing high-resolution imaging of every selected star in a transit survey,
is to model the detection pipeline's efficiency while accounting for 
binarity.
%Simply put~--~do not assume binarity can be ignored, and take the relevant 
%systematic uncertainties about the selected stars into account.
For {\it Kepler}, this would require high resolution imaging of a
comparison sample of non-KOI host stars. If the associated multiplicity 
statistics are then included in a model of the pipeline's detection 
efficiency, and the number of selected stars is appropriately counted, it 
would correct most of binarity's biases.

\paragraph{The hot Jupiter rate discrepancy}
There is at least one context in which ignoring binarity may already be 
leading to discrepant measurements.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
The discrepancy has weak statistical significance ($<3\sigma$).
One reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by \citet{gould_frequency_2006}, the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant 
planets~\citep{santos_spectroscopic_2004,fischer_planet-metallicity_2005}.
The {\it Kepler}\ sample specifically has been measured to be more metal poor 
than the local neighborhood, with a mean metallicity of $[{\rm M/H}]_{\rm 
    mean}\approx -0.05$~\citep{dong_metallicities_2014,guo_metallicity_2017}.
Studying the problem in detail, \citeauthor{guo_metallicity_2017}\! recently 
argued that the metallicity difference could account for a $\approx 20\%$ 
relative difference in the measured rates between the CKS and {\it Kepler}\ 
samples~--~not a factor of two.
\citeauthor{guo_metallicity_2017}\! concluded that ``other factors, such as 
binary contamination and imperfect stellar properties'' must also be at play.

Aside from surveying stars of varying metallicities, radial velocity and 
transit surveys differ in how they treat binarity.
Radial velocity surveys typically reject both visual and spectroscopic binaries
\citep[\textit{e.g.},][]{wright_frequency_2012}.
Transit surveys typically observe binaries, but the question of whether they 
were searchable to begin with is left for later interpretation.
In spectroscopic follow-up of candidate transiting planets, the prevalence of 
astrophysical false-positives may also lead to a bias against confirmation of 
transiting planets in binary systems.

@@

To assess the effect this might have towards resolving the hot Jupiter rate 
discrepancy we ask:
what is the probability of \citet{wright_frequency_2012}'s result, given a 
rate drawn from the stated bounds of Petigura et al.~(2018, in preparation)?
In other words, we first take the true HJ rate per thousand stars as 
$\Lambda_{\rm HJ} = 5.7 \pm 1.3$, with Gaussian uncertainties. 
We then draw from a Poisson distribution and compute the probability of 
detecting at least 10 hot Jupiters in a sample of 836 stars.
Without accounting for binarity or metallicity, only 4\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account for 
~\citet{guo_metallicity_2017}'s measured metallicity difference between the 
{\it Kepler}\ field and the local solar neighborhood, 9\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply once more by $1.3$ to account for binarity's bias, we find that
23\% of RV surveys would detect at least 10 hot Jupiters, and any discrepancy 
would be rather tenuous.
We emphasize that this result is only suggestive~--~a true resolution of the 
rate discrepancy would likely require a detailed understanding of the {\it 
Kepler}\ field's multiplicity statistics.

\paragraph{The rate of Earth analogs}
Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
orbiting Sun-like stars has been independently measured by 
\citet{youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
    foreman-mackey_exoplanet_2014}, and \citet{burke_terrestrial_2015}.
These efforts have found that the one-year terrestrial planet occurrence rate 
varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
assumptions that are made when retrieving the rate 
(\citet{burke_terrestrial_2015}'s Fig.~17).
In our Model \#3, the inferred rate is $\approx 0.84\times$ the true rate 
around single stars.
This bias is quite small compared to the other systematic factors that 
currently dominate the dispersion in $\eta_\oplus$ measurements.
If a future analyses determine absolute values of $\eta_\oplus$ to 
better than a factor of two, binarity might merit closer attention.

One relevant caveat to our assessment of binarity's importance for 
$\eta_\oplus$ measurements is that none of our models 
included the rate density's period-dependence. However, close binaries usually
provoke dynamical instabilities, leading to fewer long-period planets per 
star~\citep[\textit{e.g.},][]{holman_long-term_1999,wang_influence_2014,
    kraus_impact_2016}.
This effect might further bias transit survey measurements of $\eta_\oplus$
beyond our rough estimate.

\paragraph{Precise features of the radius valley}
\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/rate_density_vs_radius_model_4_xcut.pdf}
    \caption{
        Inferred planet occurrence rates as a function of planet radius in 
        a model with a radius gap (Eq.~\ref{eq:model4_radius_distribution}).
        Similar to Model \#3, this model has fixed primaries and single stars, 
        but varying secondaries.
    }
    \label{fig:model_4}
\end{figure}
Using improved stellar parameters measured by the California-{\it Kepler} 
survey,~\citet{fulton_california-_2017} recently reported a ``gap'' in 
the radius-period 
plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
The existence of the gap has been independently corroborated using 
asteroseismically-determined stellar 
parameters~\citep{van_eylen_asteroseismic_2017}.
Precise measurement of the gap's features, in particular its width, 
depth, and shape, requires accurate occurrence rates.
To illustrate binarity's role in the issue, we make identical assumptions as 
in Model \#3, but instead assume an intrinsic radius distribution
\begin{align}
p_r(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus, \\
0 & \text{for } 1.5r_\oplus < r < 2r_\oplus, \\
{\rm constant} & \text{for } r\leq1.5r_\oplus.
\end{cases}
\right.
\label{eq:model4_radius_distribution}
\end{align}
The resulting true and inferred rates are shown in Fig.~\ref{fig:model_4}.
If left uncorrected, binarity makes the gap more shallow, and flattens 
the step-function edges.
At present though, binarity seems less important than other effects that would 
``blur'' the gap in the planet radius dimension. 
In particular, the valley's period-dependence is almost certainly not flat
\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
This means that any study assessing its width, depth, etc. only in the planet 
radius dimension must first account for the blurring that comes from 
marginalizing over the periods.

\paragraph{Does a detected planet orbit the primary or secondary?}
\citet{ciardi_understanding_2015} studied the effects of stellar multiplicity 
on the planet radii derived from transit surveys.
They modeled the problem for {\it Kepler}\ objects of interest by matching a 
population of binary and tertiary companions to KOI stars, 
under the assumption that the KIC-listed stars were the primaries.
They then computed planet radius correction factors assuming that {\it 
Kepler}-detected planets orbited the primary or companion stars
with equal probability (their Sec. 5).
Under these assumptions, they found that any given planet's radius is on 
average underestimated by a multiplicative factor of 1.5.

Our models show that assuming a detected planet has equal probability of 
orbiting the primary or secondary leads to an overestimate of
binarity's population-level effects.
A planet orbiting the secondary does lead to extreme corrections, but these 
cases are rare outliers, because the searchable volume for secondaries is so 
much smaller than that for primaries.
Phrased in terms of the completeness, in our Model \#3 only $\sim 6\%$ of 
selected secondaries are searchable, compared to $\sim 60\%$ of selected 
primaries.
This means that when high-resolution imaging discovers a binary companion in 
a system that hosts a detected transiting planet, the planet is much
more likely to orbit the primary.
This statement is independent of the fact that planets are often confirmed to 
orbit the primary by inferring the stellar density from the transit duration.

\paragraph{On the utility for future occurrence rate measurements}
{\it TESS}\ is expected to discover over $10^4$ giant 
planets~\citep{sullivan_transiting_2015}.
Though they will be difficult to distinguish from false positives, one 
possible use of this overwhelmingly large sample will to measure an
occurrence rate of short-period giant planets.
Our work indicates that if this measurement is to be more accurate than $\sim 
30\%$, binarity cannot be neglected.

\paragraph{Independent approaches for estimating binarity's effects}
T. Barclay et al.\! (in preparation) have performed the exercise of taking 
stars selected by the {\it Kepler}\ team, pairing them with a population of 
secondaries, injecting a realistic distribution of planet radii, 
and then comparing the inferred occurrence rates with the true ones.
In their model, they find that binarity leads to an inferred rate of 
Earth-sized planets $\approx 10\%$ less than the true rate.
In our Model \#3, if all $Z_i$'s are equal (a plausible assumption in 
the lack of evidence to the contrary), the underestimate is by a comparable 
16\%.

### 2017-11-15 paper/introduction.tex
add bibtex citations; update model #4 figure

An immediate complication is that, due to dynamical stability or some 
aspect of planet formation, the occurrence rate of planets might differ 
between binary and single-star systems.
If ``occurrence rate'' is defined as the mean number of planets within 
set radius and period bounds per star in a given mass interval, it must 
implicitly marginalize over stellar multiplicity.
This means marginalizing over ``occurrence rates in single star systems'', 
``occurrence rates about primaries'', and
``occurrence rates about secondaries'' (see {\it e.g.,} Wang et al., 
2015).

@@

Correcting for binarity's observational biases is non-trivial.
For instance, in counting the number of selected stars, even after realizing 
that binaries count as two stars, one must note that the multiplicity 
fraction of {\it selected} stars is greater than that of a volume limited 
sample.
This is the familiar Malmquist bias: binaries are selected out to larger 
distances than single stars because they are more luminous.
As a separate challenge, finding the correct number of detected planets in a 
radius bin, $N_{\rm det}$, requires knowledge of the true planetary radii.
Observers deduce apparent radii.
In binaries, the apparent and true radii differ because of diluting flux, 
and possibly because the planet is assumed to orbit the wrong star ({\it 
e.g.}, Furlan et al. 2017).
%Finally, the detection efficiency $p_{\rm det}$ is different for selected 
%stars in binary systems than it is in single systems.

To gain intuition for the many observational biases at play,
we consider a set of idealized transit surveys:
\begin{itemize}
    \item Model \#1: fixed stars, fixed planets, twin binaries;
    \item Model \#2: fixed planets and primaries, varying secondaries;
    \item Model \#3: fixed primaries, varying planets and secondaries.
\end{itemize}
We define our terminology in Sec.~\ref{sec:definitions}, and present
our transit survey models in Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
each subsection corresponds to a model listed above.
We interpret these calculations throughout, and in 
Sec.~\ref{sec:discussion} connect them to topical questions in 
the interpretation of transit survey occurrence rates.
In particular, we mention the ``hot Jupiter rate discrepancy'', the relevance 
towards measurements of $\eta_\oplus$, and the significance for the dearth of 
planets recently discovered by Fulton et al. (2017).
We conclude in Sec.~\ref{sec:conclusion}

>>>>

An immediate complication is that, due to dynamical stability or some 
aspect of planet formation, the occurrence rate of planets might differ 
between binary and single-star systems.
If ``occurrence rate'' is defined as the mean number of planets within 
set radius and period bounds per star in a given mass interval, it must 
implicitly marginalize over stellar multiplicity.
This means marginalizing over ``occurrence rates in single star systems'', 
``occurrence rates about primaries'', and
``occurrence rates about secondaries''
\citep[see][]{wang_occurrence_2015}.

@@

Correcting for binarity's observational biases is non-trivial.
For instance, in counting the number of selected stars, even after realizing 
that binaries count as two stars, one must note that the multiplicity 
fraction of {\it selected} stars is greater than that of a volume limited 
sample.
This is the familiar Malmquist bias: binaries are selected out to larger 
distances than single stars because they are more luminous.
As a separate challenge, finding the correct number of detected planets in a 
radius bin, $N_{\rm det}$, requires knowledge of the true planetary radii.
Observers deduce apparent radii.
In binaries, the apparent and true radii differ because of diluting flux, 
and possibly because the planet is assumed to orbit the wrong star
\citep[\textit{e.g.},][]{furlan_kepler_2017}.

To gain intuition for the many observational biases at play,
we consider a set of idealized transit surveys:
\begin{itemize}
    \item Model \#1: fixed stars, fixed planets, twin binaries;
    \item Model \#2: fixed planets and primaries, varying secondaries;
    \item Model \#3: fixed primaries, varying planets and secondaries.
\end{itemize}
We define our terminology in Sec.~\ref{sec:definitions}, and present
our transit survey models in Secs.~\ref{sec:model_1}-\ref{sec:model_3}, where 
each subsection corresponds to a model listed above.
We interpret these calculations throughout, and in 
Sec.~\ref{sec:discussion} connect them to topical questions in 
the interpretation of transit survey occurrence rates.
In particular, we mention the ``hot Jupiter rate discrepancy'', the relevance 
towards measurements of $\eta_\oplus$, and the implications for detailed 
study of \citet{fulton_california-_2017}'s recently discovered ``valley''.
We conclude in Sec.~\ref{sec:conclusion}

### 2017-11-15 paper/model_2.tex
add bibtex citations; update model #4 figure

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of 
        binary stars, in which the underlying volume-limited distribution is 
        uniform (quite similar to {\it e.g.}, Raghavan et al. (2010)'s 
        Fig.~16).
        The entire bias can be understood analytically 
        (Eq.~\ref{eq:Malmquist_bias}).
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}

@@

We parametrize the distribution of binary mass ratios in a volume-limited 
sample as a power law: $p(q)\propto q^\beta$.
For binaries with solar-type primaries\footnote{
Duchene and Kraus (2013), fitting all the multiple systems of Raghavan et al. 
(2010)'s Fig 16, find $\beta = 0.28\pm0.05$ for $0.7<M_\star/M_\odot<1.3$.
Examining only the binary systems of Rhagavan et al 2010, Fig 16, the 
distribution seems roughly uniform, $\beta \approx 0$, except for a claimed 
excess of twin binaries with $q\approx 1$, and an obvious lack of $q<0.1$ 
stellar companions.
}, $\beta$ is probably between 0 and 0.3.
We further assume that stars are a one-parameter family, $R \propto M \propto 
L^{1/\alpha}$, so that a drawn value of $q$ determines everything about a 
secondary.

@@

There is also a Malmquist bias in Eq.~\ref{eq:model2_rate_density}, hidden 
away in the numbers of selected stars.
This is because the selected sample at a fixed planet radius and period is 
magnitude-limited.
Given a binary, the probability of drawing a mass ratio $q$ in a 
magnitude-limited sample scales as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto q^\beta 
(1+q^\alpha)^{3/2}
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the latter term is the Malmquist bias.
We show the magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Fig.~\ref{fig:q_distribn_mag_limited}.
We emphasize that in Monte Carlo simulations of transit surveys, it is 
important to draw binaries from the correctly biased mass-ratio distribution 
(e.g., Bakos et al 2012, Sullivan et al 2015, Guenther et al 2017).

>>>>

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of 
        binary stars, in which the underlying volume-limited distribution is 
        uniform (qualitatively similar to {\it 
        e.g.},~\citet{raghavan_survey_2010}'s Fig.~16).
        The entire bias can be understood analytically 
        (Eq.~\ref{eq:Malmquist_bias}).
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}

@@

We parametrize the distribution of binary mass ratios in a volume-limited 
sample as a power law: $p(q)\propto q^\beta$.
For binaries with solar-type primaries\footnote{
\citet{duchene_stellar_2013}, fitting all the multiple systems of 
\citet{raghavan_survey_2010}'s Fig 16, find $\beta = 0.28\pm0.05$ for 
$0.7<M_\star/M_\odot<1.3$.
Examining only the binary systems of \citeauthor{raghavan_survey_2010}'s Fig 
16, the distribution seems (by eye) to be roughly uniform, $\beta \approx 0$, 
except for an excess of twin binaries with $q\approx 1$, and an obvious 
lack of $q<0.1$ stellar companions.
}, $\beta$ is probably between 0 and 0.3.
We further assume that stars are a one-parameter family, $R \propto M \propto 
L^{1/\alpha}$, so that a drawn value of $q$ determines everything about a 
secondary.

@@

There is also a Malmquist bias in Eq.~\ref{eq:model2_rate_density}, hidden 
away in the numbers of selected stars.
This is because the selected sample at a fixed planet radius and period is 
magnitude-limited.
Given a binary, the probability of drawing a mass ratio $q$ in a 
magnitude-limited sample scales as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto q^\beta 
(1+q^\alpha)^{3/2}
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the latter term is the Malmquist bias.
We show the magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Fig.~\ref{fig:q_distribn_mag_limited}.
We emphasize that in Monte Carlo simulations of transit surveys, it is 
important to draw binaries from the correctly biased mass-ratio distribution 
\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
    gunther_new_2017}.

### 2017-11-15 paper/model_3.tex
add bibtex citations; update model #4 figure

As in the previous model, all single and primary stars in this model have 
identical properties.
The secondaries have masses, radii, and luminosities that vary between 
systems: $M\propto R \propto L^{1/\alpha}$.
The only addition is that we now let the radii of planets vary: they are 
assigned independently of any host system property, and are sampled from the 
true radius distribution, which we take as
\begin{align}
p_r(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus \\
{\rm constant} & \text{for } r\leq2r_\oplus.
\end{cases}
\right.
\label{eq:model3_radius_distribution}
\end{align}
Following Howard et al. (2012)'s measurement, we take $\delta = -2.92$.
Our ``nominal model'' remains the same: the binary fraction is 0.44, 
$\alpha=3.5$, $\beta=\gamma=0$.
We take $Z_i$, the number of planets per single, primary, and secondary, to be 
equal.

@@

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_3.pdf}
    \caption{
        Inferred planet occurrence rates as a function of planet radius in 
        Model 
        \#3.
        This model has fixed primaries and single stars, but varying 
        secondaries.
        The true planet radius distribution is a power law with exponent 
        $-2.92$ 
        above $2r_\oplus$, below which it is uniform ({\it e.g.}, Howard et 
        al., 
        2012).
    }
    \label{fig:errcases_model_3_log}
\end{figure}

@@

\paragraph{The rate of Earth analogs}
Our model does not explicitly include the rate density's period-dependence, 
because stellar binarity does not appreciably bias the period-dependence of 
occurrence rates measured by transit surveys\footnote{
    Note that stellar binarity does bias the {\it intrinsic} planet 
    occurrence as a function of planetary and binary periods. This is expected 
    from dynamical stability limits in $\geq$3 body systems, and has been 
    observationally confirmed (theory by Holman \& Wiegert 1999, and others 
    including Gongjie; confirmation from Wang et al 2014a, 2014b, Kraus et al 
    2014). 
    However our statement is that inferred rates as a function of planet     
    period should be negligibly affected by this, given the geometric bias 
    against long-period transit detections, and the fact that the period 
    distribution of solar-type binaries peaks at $\approx 100\,{\rm years}$ 
    (Raghavan et al 2010, Fig.~13).
}.
Instead, it allows us to evaluate the difference in the apparent and true rate 
as a function of radius 
(Fig.~\ref{fig:errcases_model_3_log}).
At Earth's radius, the result is that the inferred rate is $0.84\times$ the 
true rate around single stars, assuming that the $Z_i$'s are equal.
Similar to the above case of the hot Jupiters, if we vary the true $Z_2$ 
while keeping $Z_0 = Z_1$, the ratio of the inferred to true rate 
around single stars changes by only a few percent (shown in 
Fig.~\ref{fig:earth_inputrate_vs_etaearthratevalues}).
The ratio of the inferred to the true rate, $(\Lambda_{\rm 
inferred}/\Lambda)_{r=r_\oplus}$ varies substantially, but by at most $50\%$ 
in the (unrealistic) limiting case that secondaries do not host planets.

>>>>

As in the previous model, all single and primary stars in this model have 
identical properties.
The secondaries have masses, radii, and luminosities that vary between 
systems: $M\propto R \propto L^{1/\alpha}$.
The only addition is that we now let the radii of planets vary: they are 
assigned independently of any host system property, and are sampled from the 
true radius distribution, which we take as
\begin{align}
p_r(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus \\
{\rm constant} & \text{for } r\leq2r_\oplus.
\end{cases}
\right.
\label{eq:model3_radius_distribution}
\end{align}
Following~\citet{howard_planet_2012}'s measurement, we take $\delta = -2.92$.
Our ``nominal model'' remains the same: the binary fraction is 0.44, 
$\alpha=3.5$, $\beta=\gamma=0$.
We take $Z_i$, the number of planets per single, primary, and secondary, to be 
equal.

@@

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_3.pdf}
    \caption{
        Inferred planet occurrence rates as a function of planet radius in 
        Model 
        \#3.
        This model has fixed primaries and single stars, but varying 
        secondaries.
        The true planet radius distribution is a power law with exponent 
        $-2.92$ 
        above $2r_\oplus$, below which it is uniform \citep[similar 
        to][]{howard_planet_2012}.
    }
    \label{fig:errcases_model_3_log}
\end{figure}

@@

\paragraph{The rate of Earth analogs}
This model provides an estimate of the apparent and true 
rates as a function of radius (Fig.~\ref{fig:errcases_model_3_log}).
At Earth's radius, the result is that the inferred rate is $0.84\times$ the 
true rate around single stars, assuming that the $Z_i$'s are equal.
Similar to the above case of the hot Jupiters, if we vary the true $Z_2$ 
while keeping $Z_0 = Z_1$, the ratio of the inferred to true rate 
around single stars changes by only a few percent (shown in 
Fig.~\ref{fig:earth_inputrate_vs_etaearthratevalues}).
The ratio of the inferred to the true rate, $(\Lambda_{\rm 
    inferred}/\Lambda)_{r=r_\oplus}$ varies substantially, but by at most 
    $50\%$ 
in the (unrealistic) limiting case that secondaries do not host planets.
